### 2018-04-16 paper/paper.tex
add .tex file

\documentclass[a4paper]{article}
\usepackage{amsmath, bm}
\usepackage[margin=1in]{geometry}
\begin{document}
\section{Linear Regression}
\subsection{Derivation of Regularized Linear Regression}
asdfasdf

\section{Logistic Regression}
\subsection{Derivation of Gradient}
\begin{equation}
\begin{split}
J(\bm{\theta}) &= -\frac{1}{m} \sum_{i=1}^{m} \left( y^{(i)} \log (h_{\bm{\theta}}(\bm{x}^{(i)}))
+ (1-y^{(i)} ) \log (1 - h_{\bm{\theta}}(\bm{x}^{(i)}))  \right) \\
&=  -\frac{1}{m} \sum_{i=1}^{m} \left( y^{(i)} \log (\sigma(\bm{x}^{(i)T}\bm{\theta}))
+ (1-y^{(i)} ) \log (1 - \sigma(\bm{x}^{(i)T}\bm{\theta})  \right)
\end{split}
\end{equation}
The partial derivative of the cost function with respect $\theta_j$ is
\begin{equation}
\begin{split}
\frac{\partial J(\bm{\theta})}{\partial \theta_j }
&= -\frac{1}{m} \sum_{i=1}^m \left(
y^{(i)} \frac{1}{\sigma(\bm{x}^{(i)T}\bm{\theta})} \frac{\partial \sigma(\bm{x}^{(i)T}\bm{\theta})}{\partial \theta_j}
- (1-y^{(i)}) \frac{1}{1-\sigma(\bm{x}^{(i)T}\bm{\theta})} \frac{\partial \sigma(\bm{x}^{(i)T}\bm{\theta})}{\partial \theta_j}
\right) \\
&= -\frac{1}{m} \sum_{i=1}^m \left(
y^{(i)} \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta}))}{\sigma(\bm{x}^{(i)T}\bm{\theta})} \cdot \frac{\partial \bm{x}^{(i)T}\bm{\theta}}{\partial \theta_j}
 - (1 - y^{(i)}) \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta}))}{1 - \sigma(\bm{x}^{(i)T}\bm{\theta})} \cdot \frac{\bm{x}^{(i)T}\bm{\theta}}{\partial \theta_j}
\right) \\
&= -\frac{1}{m} \sum_{i=1}^{m} \left(
y^{(i)} \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta})) \cdot x_j^{(i)}}{\sigma(\bm{x}^{(i)T}\bm{\theta})}
- (1 - y^{(i)}) \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta})) \cdot x_j^{(i)}}{1 - \sigma(\bm{x}^{(i)T}\bm{\theta})}
\right) \\
&= - \frac{1}{m} \sum_{i=1}^m \left(
y^{(i)} - y^{(i)} \sigma(\bm{x}^{(i)T}\bm{\theta}) + y^{(i)} \sigma(\bm{x}^{(i)T}\bm{\theta}) - \sigma(\bm{x}^{(i)T}\bm{\theta}) \right)\cdot x_j^{(i)} \\
&= -\frac{1}{m} \sum_{i=1}^m \left(
y^{(i)} - \sigma(\bm{x}^{(i)T}\bm{\theta})\right) \cdot x_j^{(i)} \\
&= \frac{1}{m} \sum_{i=1}^m \left( h_{\bm{\theta}}(\bm{x}^{(i)}) - y^{(i)}\right) \cdot x_j^{(i)}
\end{split}
\end{equation}
Thus, the gradient of the cost function is
\begin{equation}
\frac{\partial J(\bm{\theta})}{\partial \theta_j } = \frac{1}{m} \sum_{i=1}^m \left( h_{\bm{\theta}}(\bm{x}^{(i)}) - y^{(i)}\right) \cdot x_j^{(i)}
\end{equation}
\end{document}

### 2018-04-16 main_rbf_model_selection.py
completes additional rbf functions

@@ -54,7 +54,10 @@ def main():
     n_centers = np.arange(K) + 1
 
     # Compute the MSE values
-    i_best = 0
+    for i in range(K):
+        theta_list[i], mse_train[i], mse_val[i], mse_test[i] = rbf.train_and_test(data, n_centers[i])
+
+    i_best = np.argmin(mse_val)
 
     #
     # TODO END

### 2018-04-16 poly.py

@@ -34,7 +34,6 @@ def design_matrix(x, degree):
     :return: Expanded data in a numpy array of shape (N,degree+1)
     """
 
-
     power_arrays = []
     for i in range(degree + 1):
         power_arrays.append(x**i)

### 2018-04-16 rbf.py

@@ -37,8 +37,8 @@ def get_centers_and_sigma(n_centers):
     #       an euclidian division. The solution is to convert one of the two integers to float.
     #
 
-    centers = np.zeros(n_centers)  # TODO: Change me
-    sigma = 1.  # TODO: Change me
+    centers = np.linspace(-1.0, 1.0, n_centers)
+    sigma = 2.0 / n_centers
 
     # END TODO
     ######################
@@ -76,7 +76,12 @@ def design_matrix(x, centers, sigma):
     # TIP: don't forget that the first row has only ones
     #
 
-    res = x  # TODO: Change me
+    hbf_arrays = [x]
+    for c in centers:
+        new_arr = np.exp(((x - c)**2 * -1) / (2 * sigma**2))
+        hbf_arrays.append(new_arr)
+
+    res = np.hstack(hbf_arrays)
 
     # END TODO
     ######################
@@ -107,7 +112,9 @@ def train(x, y, n_centers):
     #   - This should not be very different from the solution you provided in poly.py
     #
 
-    theta_opt = np.zeros(n_centers + 1)  # TODO: Change me
+    centers, sigma = get_centers_and_sigma(n_centers)
+    X = design_matrix(x, centers, sigma)
+    theta_opt = np.linalg.inv(X.T.dot(X)).dot(X.T.dot(y))
 
     # END TODO
     ######################
@@ -138,7 +145,9 @@ def compute_error(theta, n_centers, x, y):
     #   - This should not be very different from the solution you provided in poly.py
     #
 
-    err = -1  # TODO: Change me
+    centers, sigma = get_centers_and_sigma(n_centers)
+    X = design_matrix(x, centers, sigma)
+    err = np.linalg.norm(X.dot(theta) - y) ** 2
 
     # END TODO
     ######################

### 2018-04-16 plot_rbf.py
completes plot_rbf.plot_errors function

@@ -92,7 +92,15 @@ def plot_errors(i_best, n_centers, mse_train, mse_val, mse_test):
     # Tips:
     #  - Don't forget to make everything readable with legend title
 
-    plt.plot(n_centers, n_centers, label='Change me', linewidth=3)
+    for mse, lab in zip([mse_train, mse_val, mse_test], ['train', 'val', 'test']):
+        plt.plot(n_centers, mse/np.max(mse), label=lab, linewidth=3)
+
+    plt.ylim([0, 1])
+    plt.axvline(x=n_centers[i_best], color='black', linestyle='--', linewidth=3,
+                label='Optimal degree {}'.format(n_centers[i_best]))
+    plt.xlabel('Degrees')
+    plt.ylabel('MSE')
+    plt.legend()
 
     #
     # END TODO

### 2018-04-16 paper/paper.tex
add title page
edit indent

@@
 \usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
 \begin{document}
+\begin{titlepage}
+  \centering
+    {\huge \bf Assignment 1\par}
+    \vspace{1cm}
+    {\Large Computational Intelligence, SS2018\par}
+    \vspace{1cm}
+    \begin{tabular}{|l|l|l|}
+      \hline
+      \multicolumn{3}{|c|}{\textbf{Team Members}}   \\ \hline
+      Last name & First name & Matriculation Number \\ \hline
+      Lee       & Eunseo     & 11739623             \\ \hline
+      Shadley   & Alex       & 11739595             \\ \hline
+      Lee       & Dayeong    & 11730321             \\ \hline
+    \end{tabular}
+\end{titlepage}
+
 \section{Linear Regression}
@@
 asdfasdf
+
+\subsection{Linear Regression with polynomial features}
+
+The following plots demonstrate the results of Linear Regression with polynomial degrees of 1, 2, 5, and 20:
+
+\noindent
+\includegraphics[width=0.5\textwidth]{linreg_deg1.png}%
+\includegraphics[width=0.5\textwidth]{linreg_deg2.png}\\[2em]
+\includegraphics[width=0.5\textwidth]{linreg_deg5.png}%
+\includegraphics[width=0.5\textwidth]{linreg_deg20.png}\par
 
@@
 \end{equation}
+\subsection{Logistic Regression training with gradient descent and scipy.optimize}
+\subsubsection{Gradient descent}
+\paragraph
+1The function check\_gradient in toolbox.py is here to test if your gradient is well computed. Explain what it is doing
+\paragraph
+2The following plots demonstrate the results of Logistic Regression with degree 1 and learning rate $\eta$ = 1 for 20 and 2000 iterations :
+
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter20.png}
+	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter20_error.png}
+	\caption{iteration = 20}
+\end{figure}
+\clearpage
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter2000.png}
+	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter2000_error.png}
+	\caption{iteration = 2000}
+\end{figure}
+
+In the case of figure 1, the process stops before it reaches the local minima.
+In the case of figure 2, the process reaches the local minima in about 50 iterations.
+However, it continues to iterate even though the error does not change.
+
+When the number of iterations is too low, the logistic regression process finishes before reaching the local minima.When the number of iterations is too high, it takes a lot of time.
+Even though it reaches the local minima, it continues to iterate until it reaches the iteration number.
+Therefore, the number of iterations should not be too low and high.
+\paragraph
+3 The following plots demonstrate the results of Logistic Regression with degree = 2 , iterations = 200 and learning rate $\eta$ = \{.15, 1.5, 15.\} :
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta015.png}
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta015_error.png}
+	\caption{learing rate $\eta$ = .15}
+\end{figure}
+\clearpage
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta105.png}
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta105_error.png}
+	\caption{learing rate $\eta$ = 1.5}
+\end{figure}
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta15.png}
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta15_error.png}
+	\caption{learing rate $\eta$ = 15}
+\end{figure}
+
+In the case of figure 3, the process stops before it reaches the local minima.
+In the case of figure 4, the process reaches the local minima.
+In the case of figure 5, it doesn't reach the local minima by overshooting the local minima.
+
+When learning rate is too low, it takes a lot of time to reach the local minima or it ends before reaching the local minima.
+When learning rate is too big, it can overshoot the local minima so it may not reach the local minima or may even diverge.
+
+\paragraph
+4
+\paragraph
+5 One possible way to terminate the gradient descent is setting a threshold to the cost function.
+While caluating the cost in each iteration, if it is below the setting threshold, it can terminate the process.
+Using this way, it can not reach the perfect local minima but it can reach close to the local minima depending on the threshold.
+Therefore it can save time.
+If high accuracy is aimed, then set the threshold low.
+And if middle accuracy and high speeed are aimed, then set the threshold a little bit higher.
+\subsubsection{Adaptative gradient descent (GDad)}
+\paragraph
+1 The following plots demonstrate the results of Logistic Regression with iterations = 1000, learning rate $\eta$ = 1 and varying degrees $l$ = \{1, 2, 5, 15\}:
+
+\begin{figure}[h]
+	\includegraphics[width=0.4	\textwidth]{logreg_deg1_iter20000.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg1_iter20000_learn.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg1_iter20000_error.png}
+	\textbf{final learning rate : 2.59$e$\textsuperscript{-132}}
+	\caption{degree $l$ = 1}
+\end{figure}
+	\begin{figure}[h]
+	\includegraphics[width=0.4	\textwidth]{logreg_deg2_iter2000.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter2000_learn.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter2000_error.png}
+	\textbf{final learning rate : 3.94$e$\textsuperscript{-274}}
+	\caption{degree $l$ = 2}
+\end{figure}
+\begin{figure}[h]
+	\includegraphics[width=0.4\textwidth]{logreg_deg5_iter2000.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg5_iter2000_learn.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg5_iter2000_error.png}
+	\textbf{final learning rate : 12.5}
+	\caption{degree $l$ = 5}
+\end{figure}
+\begin{figure}[h]
+	\includegraphics[width=0.4\textwidth]{logreg_deg15_iter2000.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg15_iter2000_learn.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg15_iter2000_error.png}
+	\textbf{final learning rate : 12.5}
+	\caption{degree $l$ = 15}
+\end{figure}
+\clearpage
+\paragraph
+2  These are the comparsion between GDad and non-adpative GD.\\
+\textbf{Degree $l$ = 1 :}\\
+Speed : GDad reaches near the local minima faster than non-adaptive gradient.\\
+Train set error : Both have the same train error(0.469).\\
+Test set error : Both have the same test error(0.387).\\
+\\
+\textbf{Degree $l$ = 2 :}\\
+Speed : GDad reaches near the local minima faster than non-adaptive gradient.\\
+Train set error : Both have the same train error(0.450).\\
+Test set error : Both have the same test error(0.354).\\
+\\
+\textbf{Degree $l$ = 5 :}\\
+Spped : GDad reaches near the local minima faster than non-adaptive gradient.\\
+Train set error : GDad have smaller train error(0.315) than non-adaptive GD(0.349).\\
+Test set error : GDad have bigger test error(0.353) than non-adaptive GD(0.323).\\
+\\
+\textbf{Degree $l$ = 15 :}\\
+Spped : GDad reaches near the local minima faster than non-adaptive gradient.\\
+Train set error : GDad have smaller train error(0.303) than non-adaptive GD(0.333).\\
+Test set error : GDad have bigger test error(0.390) than non-adaptive GD(0.342).\\
+\\
+\\
+The evolution of the learning rate is something different from my previous guess of the optimal learning rate.
+I thought that the evolution of the learning rate looks like a mountain.
+It is true in the case of degree 1 and 2.
+However, in the case of degree 5 and 15, the graph vibrates at the latter part because of the overshooting problem.
+\\
+\\
+GDad is more useful than non-adaptive gradient descent in the respect of the speed(when the learning rate is small) and overshooting the minima(when the learning rate is big). \\
+First, GDad can reach the local minima faster than non-adaptive gradient descent.
+When the learning rate is small, gradient descent should iterate more than GDad to reach the local minima.
+Because, in the case of GDad, the learning rate becomes large when the cost becomes small and can make a big step to the local minima.\\
+Second, GDad can avoid the overshooting problem.
+When the learning rate is big, it can suffer from overshooting problem because the process makes a big step, roams near the local minima and can not reach the local minima.
+In this case, the costs becomes large and GDad notices that it is in overshooting problem.
+Then, it can avoid overshooting problem by decreasing the learning rate and reach the local minima.
+\\
+That is, at fist, GDad makes big steps to find the the local minima.
+Then, when it reaches near the local minima, it decreases the learning rate to avoid the overshooting problem and reachs the local minima.
+
+\subsubsection{Scipy optimizer}
+\paragraph
+1 The following plots demonstrate the results of Logistic Regression using scipy.optimize, with iterations = 1000, learning rate $\eta$ = 1 and varying degrees $l$ = \{1, 2, 5, 15\}:
+\begin{figure}[h]
+	\includegraphics[width=0.4\textwidth]{scipy_1.png}
+	\caption{degree $l$ = 1}
+	\includegraphics[width=0.4\textwidth]{scipy_2.png}
+	\caption{degree $l$ = 2}
+	\includegraphics[width=0.4\textwidth]{scipy_5.png}
+	\caption{degree $l$ = 5}
+	\includegraphics[width=0.4\textwidth]{scipy_15.png}
+	\caption{degree $l$ = 15}
+\end{figure}
+\clearpage
+
+\paragraph
+2 These are the comparsion between GDad, non-adpative GD and scipy optimizer.\\
+\textbf{Degree $l$ = 1 :}\\
+Train set error : All have the same train error(0.469).\\
+Test set error : All have the same test error(0.387).\\
+\\
+\textbf{Degree $l$ = 2 :}\\
+Train set error : All have the same train error(0.450).\\
+Test set error : All have the same test error(0.354).\\
+\\
+\textbf{Degree $l$ = 5 :}\\
+Train set error : Scipy optimizer(0.295) $<$ GDad (0.315) $<$ GD(0.349).\\
+Test set error : Scipy optimizer(0.417) $>$ GDad(0.353) $>$ GD(0.323).\\
+\\
+\textbf{Degree $l$ = 15 :}\\
+Train set error : Scipy optimizer(0.210) $<$ GDad(0.303) $<$ GD(0.333).\\
+Test set error : Scipy optimizer(1.649) $<$ GDad (0.390) $<$ non-adaptive GD(0.342).\\
+\\
+Scipy optimizer optimizes the cost function better than the others.
+Therefore it has the lowest train set errors in all degrees.
+However, it has the highest test set error in all degrees.
+I think it is becuase of overfitting to the train set.
+Scipy optimizer makes a hypothesis fit perfectly to train set so it causes overfitting problem and get the highest test set error.\\
+\\
+It doesn't change my opinion that degree $l$ = 5 is best to fit the data.
+Low degree can not predict the complex hypothesis and high degree can cause the overfitting problem.
+Therfore, appropriate degree is the best.
+In this problem, it is 5.
+
 \end{document}

### 2018-04-16 main_poly.py
fixes improperly calculated error

@@ -23,7 +23,7 @@ TODO boxes are to be found in 'poly.py'
 
 def main():
     # Set the degree of the polynomial expansion
-    degree = 5
+    degree = 20
     data_path = 'data_linreg.json'
 
     # Load the data

### 2018-04-16 plot_poly.py

@@ -80,7 +80,7 @@ def plot_errors(i_best, degrees, mse_train, mse_val, mse_test):
     """
 
     for mse, lab in zip([mse_train, mse_val, mse_test], ['train', 'val', 'test']):
-        plt.plot(degrees, mse/np.max(mse), label=lab, linewidth=3)
+        plt.plot(degrees, mse, label=lab, linewidth=3)
 
     plt.ylim([0, 1])
     plt.axvline(x=degrees[i_best], color='black', linestyle='--', linewidth=3,

### 2018-04-16 paper/paper.tex
adds figures to paper

--- 2018-04-16 paper/paper.tex
@@
 \usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
 \begin{document}
+\begin{titlepage}
+	\centering
+	{\huge \bf Assignment 1\par}
+	\vspace{1cm}
+	{\Large Computational Intelligence, SS2018\par}
+	\vspace{1cm}
+	\begin{tabular}{|l|l|l|}
+	\hline
+	\multicolumn{3}{|c|}{\textbf{Team Members}}   \\ \hline
+	Last name & First name & Matriculation Number \\ \hline
+	Lee       & Eunseo     & 11739623             \\ \hline
+	Shadley   & Alex       & 11739595             \\ \hline
+	          &            &                      \\ \hline
+	\end{tabular}
+\end{titlepage}
+
 \section{Linear Regression}

### 2018-04-17 logreg.py
implement cost function in logreg.py

@@ -1,6 +1,6 @@
 #!/usr/bin/env python
 import numpy as np
-
+from math import log
 from logreg_toolbox import sig
 
 __author__ = 'bellec, subramoney'
@@ -24,23 +24,15 @@ def cost(theta, x, y):
     """
     N, n = x.shape
 
-    ##############
-    #
-    # TODO
-    #
-    # Write the cost of logistic regression as defined in the lecture
-    # Hint:
-    #   - use the logistic function sig imported from the file toolbox
-    #   - sums of logs of numbers close to zero might lead to numerical errors, try splitting the cost into the sum
-    # over positive and negative samples to overcome the problem. If the problem remains note that low errors is not
-    # necessarily a problem for gradient descent because only the gradient of the cost is used for the parameter updates.
-
     c = 0
-
-    # END TODO
-    ###########
-
-    return c
+    h = sig(np.matmul(x, theta))
+    for hi, yi in zip(h, y) :
+        if yi == 0:
+            c += -1 * log(1-hi)
+        else:
+            c += -1 * log(hi)
+    c = c/N
+    return np.array([c])
 
 
 def grad(theta, x, y):

### 2018-04-17 logreg.py
implement gradient funciton in logreg.py

@@ -32,7 +32,8 @@ def cost(theta, x, y):
         else:
             c += -1 * log(hi)
     c = c/N
-    return np.array([c])
+
+    return np.array([c]) 
 
 
 def grad(theta, x, y):
@@ -46,15 +47,8 @@ def grad(theta, x, y):
     :return: gradient
     """
     N, n = x.shape
-
-    ##############
-    #
-    # TODO
-    #
-
-    g = np.zeros(theta.shape)
-
-    # END TODO
-    ###########
+    
+    h = sig(np.matmul(x, theta))-y
+    g = np.matmul(h.T, x)/N
 
     return g

### 2018-04-17 gradient_descent.py
implement adaptive_gradient_descent

@@ -59,18 +59,20 @@ def adaptative_gradient_descent(f, df, theta0, initial_learning_rate, max_iter):
     :return: x (solution), E_list (list of errors), lr_list (the list of learning rates)
     """
 
-    ##############
-    #
-    # TODO
-    #
-    # Implement the adaptive gradient descent algorithm
-    #
-
-    E_list = np.zeros(max_iter)
-    lr_list = np.zeros(max_iter)
+    E_list = np.zeros(max_iter+1)
+    lr_list = np.zeros(max_iter+1)
+    
     theta = theta0
-
-    # END TODO
-    ###########
-
+    E_list[0] = f(theta0)
+    lr_list[0] = initial_learning_rate
+    
+    for i in range(0,max_iter):
+        new_theta = theta - lr_list[i] * df(theta)
+        E_list[i+1] = f(new_theta)
+        if E_list[i+1] < E_list[i]:
+            lr_list[i+1] = lr_list[i] * 1.03
+            theta = new_theta
+        else:
+            lr_list = lr_list[i] * 0.7
+   
     return theta, E_list, lr_list

### 2018-04-17 paper/paper.tex
update the answer of 2.2.2/2.2.3

@@
 	Shadley   & Alex       & 11739595             \\ \hline
-	          &            &                      \\ \hline
+	Lee       & Dayeong    & 11730321             \\ \hline
 	\end{tabular}
@@
 \end{equation}
+\subsection{Logistic Regression training with gradient descent and scipy.optimize}
+\subsubsection{Gradient descent}
+\paragraph
+1The function check\_gradient in toolbox.py is here to test if your gradient is well computed. Explain what it is doing
+\paragraph
+2The following plots demonstrate the results of Logistic Regression with degree 1 and learning rate $\eta$ = 1 for 20 and 2000 iterations :
+
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter20.png}
+	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter20_error.png}
+	\caption{iteration = 20}
+\end{figure}
+\clearpage
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter2000.png}
+	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter2000_error.png}
+	\caption{iteration = 2000}
+\end{figure}
+
+In case of figure 1, the process stops before it reaches the local minima.
+In case of figure 2, the process reaches the local minima in about 50 iterations.
+However, it continues to iterate even though the error does not change.
+
+When the number of iterations is too low, the logistic regression process finishes before reaching the local minima.When the number of iterations is too high, it takes a lot of time.
+Even though it reaches the local minima, it continues to iterate until it reaches the iteration number.
+Therefore, the number of iterations should not be too low and high.
+\paragraph
+3 The following plots demonstrate the results of Logistic Regression with degree = 2 , iterations = 200 and learning rate $\eta$ = \{.15, 1.5, 15.\} :
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta015.png}
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta015_error.png}
+	\caption{learing rate $\eta$ = .15}
+\end{figure}
+\clearpage
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta105.png}
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta105_error.png}
+	\caption{learing rate $\eta$ = 1.5}
+\end{figure}
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta15.png}
+	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta15_error.png}
+	\caption{learing rate $\eta$ = 15}
+\end{figure}
+
+In case of figure 3, the process stops before it reaches the local minima.
+In case of figure 4, the process reaches the local minima.
+In case of figure 5, it doesn't reach the local minima by overshooting the local minima.
+
+When learning rate is too low, it takes a lot of time to reach the local minima or it ends before reaching the local minima.
+When learning rate is too big, it can overshoot the local minima so it may not reach the local minima or may even diverge.
+
+\paragraph
+4
+\paragraph
+5
 \end{document}

### 2018-04-17 gradient_descent.py
Fix an error in adaptive_gradient_descent

@@ -73,6 +73,6 @@ def adaptative_gradient_descent(f, df, theta0, initial_learning_rate, max_iter):
             lr_list[i+1] = lr_list[i] * 1.03
             theta = new_theta
         else:
-            lr_list = lr_list[i] * 0.7
+            lr_list[i+1] = lr_list[i] * 0.7
    
     return theta, E_list, lr_list

### 2018-04-17 paper/paper.tex
Update the answer 2.2.2.1

@@
 5
+
+\subsubsection{Adaptative gradient descent (GDad)}
+\paragraph
+1 The following plots demonstrate the results of Logistic Regression with iterations = 2000, learning rate $\eta$ = 1 and varying degrees $l$ = \{1, 2, 5, 15\}:
+\begin{figure}[h]	
+	\includegraphics[width=0.4	\textwidth]{logreg_deg1_iter20000.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg1_iter20000_learn.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg1_iter20000_error.png}
+	\textbf{final learning rate : 3.25$e$\textsuperscript{-287}}
+	\caption{degree $l$ = 1}
+\end{figure}
+\begin{figure}[h]	
+\includegraphics[width=0.4	\textwidth]{logreg_deg2_iter2000.png}
+\includegraphics[width=0.4\textwidth]{logreg_deg2_iter2000_learn.png}
+\includegraphics[width=0.4\textwidth]{logreg_deg2_iter2000_error.png}
+\textbf{final learning rate : 3.94$e$\textsuperscript{-274}}
+\caption{degree $l$ = 2}
+\end{figure}
+\begin{figure}[h]	
+\includegraphics[width=0.4\textwidth]{logreg_deg5_iter2000.png}
+\includegraphics[width=0.4\textwidth]{logreg_deg5_iter2000_learn.png}
+\includegraphics[width=0.4\textwidth]{logreg_deg5_iter2000_error.png}
+\textbf{final learning rate : 15.3}
+\caption{degree $l$ = 5}
+\end{figure}
+\begin{figure}[h]	
+	\includegraphics[width=0.4\textwidth]{logreg_deg15_iter2000.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg15_iter2000_learn.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg15_iter2000_error.png}
+	\textbf{final learning rate : 10.4}
+	\caption{degree $l$ = 15}
+\end{figure}
+
+For each degree compare with the non-adaptive gradient descent variant.
+In particular, is the evolution of the learning rate numerically coherent with your previous guess of the optimal learning rate ?
+Discuss why GDad can be useful.
+
 \end{document}

### 2018-04-17 paper/paper.tex
update the answer of 2.2.2.2

@@
 
-In case of figure 1, the process stops before it reaches the local minima.
-In case of figure 2, the process reaches the local minima in about 50 iterations.
+In the case of figure 1, the process stops before it reaches the local minima.
+In the case of figure 2, the process reaches the local minima in about 50 iterations.
 However, it continues to iterate even though the error does not change.
@@
 
-In case of figure 3, the process stops before it reaches the local minima.
-In case of figure 4, the process reaches the local minima.
-In case of figure 5, it doesn't reach the local minima by overshooting the local minima.
+In the case of figure 3, the process stops before it reaches the local minima.
+In the case of figure 4, the process reaches the local minima.
+In the case of figure 5, it doesn't reach the local minima by overshooting the local minima.
 
@@
 1 The following plots demonstrate the results of Logistic Regression with iterations = 2000, learning rate $\eta$ = 1 and varying degrees $l$ = \{1, 2, 5, 15\}:
+
 \begin{figure}[h]	
@@
 \end{figure}
-
-For each degree compare with the non-adaptive gradient descent variant.
-In particular, is the evolution of the learning rate numerically coherent with your previous guess of the optimal learning rate ?
-Discuss why GDad can be useful.
+\clearpage
+\paragraph
+2  These are the comparsion between GDad and non-adpative GD.
+\textbf{Degree $l$ = 1 :}\\
+Speed : GDad reaches near the local minima faster than non-adaptive gradient.\\
+Train set error : Both have the same train error(0.469).\\
+Test set error : Both have the same test error(0.387).\\
+\\ 
+\textbf{Degree $l$ = 2 :}\\
+Speed : GDad reaches near the local minima faster than non-adaptive gradient.\\
+Train set error : Both have the same train error(0.450).\\
+Test set error : Both have the same test error(0.354).\\
+\\
+\textbf{Degree $l$ = 5 :}\\
+Spped : GDad reaches near the local minima faster than non-adaptive gradient.\\
+Train set error : GDad have smaller train error(0.308) than non-adaptive GD(0.336).\\
+Test set error : GDad have bigger test error(0.359) than non-adaptive GD(0.328).\\
+\\
+\textbf{Degree $l$ = 15 :}\\
+Spped : GDad reaches near the local minima faster than non-adaptive gradient.\\
+Train set error : GDad have smaller train error(0.209) than non-adaptive GD(0.323).\\
+Test set error : GDad have bigger test error(0.399) than non-adaptive GD(0.357).\\
+\\
+\\
+The evolution of the learning rate is something different from my previous guess of the optimal learning rate.
+I thought that the evolution of the learning rate looks like a mountain.
+It is true in the case of degree 1 and 2.
+However, in the case of degree 5 and 15, the graph vibrates at the latter part because of the overshooting problem.
+\\
+\\
+GDad is more useful than non-adaptive gradient descent in the respect of the speed(when the learning rate is small) and overshooting the minima(when the learning rate is big). \\
+First, GDad can reach the local minima faster than non-adaptive gradient descent.
+When the learning rate is small, gradient descent should iterate more than GDad to reach the local minima.
+Because, in the case of GDad, the learning rate becomes large when the cost becomes small and can make a big step to the local minima.\\
+Second, GDad can avoid the overshooting problem.
+When the learning rate is big, it can suffer from overshooting problem because the process makes a big step, roams near the local minima and can not reach the local minima.
+In this case, the costs becomes large and GDad notices that it is in overshooting problem.
+Then, it can avoid overshooting problem by decreasing the learning rate and reach the local minima.
+\\
+That is, at fist, GDad makes big steps to find the the local minima.
+Then, when it reaches near the local minima, it decreases the learning rate to avoid the overshooting problem and reachs the local minima.
 

### 2018-04-17 paper/paper.tex
answer for preliminary questions in 1.1

@@
 \documentclass[a4paper]{article}
-\usepackage{amsmath, bm}
+\usepackage{amsmath, amssymb, bm}
 \usepackage[margin=1in]{geometry}
@@
 \subsection{Derivation of Regularized Linear Regression}
-asdfasdf
+\begin{itemize}
+  \item Preliminary questions
+    \begin{itemize}
+      \item for each i, \(\bm{X}^{(i)}\) is n+1 dimensional column vector. For
+        notaion convenience, all \(\bm{X}_0^{(i)}\) is set to \(0\).
+      \item The gradient of \(J(\bm{\theta})\) is \[
+          \frac{\partial J(\bm{\theta})}{\partial \bm{\theta}} = \langle
+          \frac{\partial J(\bm{\theta})}{\partial \theta_0}, \quad
+          \frac{\partial J(\bm{\theta})}{\partial \theta_1}, \quad
+          \cdots, \quad
+          \frac{\partial J(\bm{\theta})}{\partial \theta_n}
+          \rangle
+        \]. It is n+1 dimensional column vector.
+      \item In gradient, function \(f\) is
+        \(\mathbb{R}^n\rightarrow\mathbb{R} \) and the gradient itself is vector.
+        The jacobian matrix of function
+        \(\bm{f}\colon\mathbb{R}^n\rightarrow\mathbb{R}^m\) is
+        \[[
+          \quad \frac{\partial \bm{f}}{\partial x_1} \quad
+          \frac{\partial \bm{f}}{\partial x_2} \quad
+          \cdots \quad \frac{\partial \bm{f}}{\partial x_n} \quad
+          ] =
+          \begin{bmatrix}
+            \frac{\partial f_1}{\partial x_1} & \cdots & \frac{\partial f_1}{\partial x_n} \\
+            \vdots & \ddots & \vdots \\
+            \frac{\partial f_m}{\partial x_1} & \cdots & \frac{\partial f_m}{\partial x_n}
+          \end{bmatrix}
+          \]
+          where \(\bm{f} = <f_1, f_2, \cdots, f_m>\) and \(\bm{x} = <x_1, x_2, \cdots, x_n>\).
+          When \(m=0\), Jacobian matrix and gradient are same.
+        \item \(\bm{X\theta}\) is \(m\) dimension vector. The dimension of jacobian
+          matrix \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is \(n+1 \times m\).
+          In this case, \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is same with \(\bm{X}\).
+    \end{itemize}
+  \item 2
+  \item 3
+\end{itemize}
 
@@
 \paragraph
-5
-
+5 One possible way to terminate the gradient descent is setting a threshold to the cost function.
+While caluating the cost in each iteration, if it is below the setting threshold, it can terminate the process.
+Using this way, it can not reach the perfect local minima but it can reach close to the local minima depending on the threshold.
+Therefore it can save time.
+If high accuracy is aimed, then set the threshold low.
+And if middle accuracy and high speeed are aimed, then set the threshold a little bit higher.
 \subsubsection{Adaptative gradient descent (GDad)}
 \paragraph
-1 The following plots demonstrate the results of Logistic Regression with iterations = 2000, learning rate $\eta$ = 1 and varying degrees $l$ = \{1, 2, 5, 15\}:
+1 The following plots demonstrate the results of Logistic Regression with iterations = 1000, learning rate $\eta$ = 1 and varying degrees $l$ = \{1, 2, 5, 15\}:
 
@@
 	\includegraphics[width=0.4\textwidth]{logreg_deg1_iter20000_error.png}
-	\textbf{final learning rate : 3.25$e$\textsuperscript{-287}}
+	\textbf{final learning rate : 2.59$e$\textsuperscript{-132}}
 	\caption{degree $l$ = 1}
@@
 	\includegraphics[width=0.4\textwidth]{logreg_deg5_iter2000_error.png}
-	\textbf{final learning rate : 15.3}
+	\textbf{final learning rate : 12.5}
 	\caption{degree $l$ = 5}
@@
 	\includegraphics[width=0.4\textwidth]{logreg_deg15_iter2000_error.png}
-	\textbf{final learning rate : 10.4}
+	\textbf{final learning rate : 12.5}
 	\caption{degree $l$ = 15}
@@
 \paragraph
-2  These are the comparsion between GDad and non-adpative GD.
+2  These are the comparsion between GDad and non-adpative GD.\\
 \textbf{Degree $l$ = 1 :}\\
@@
 Spped : GDad reaches near the local minima faster than non-adaptive gradient.\\
-Train set error : GDad have smaller train error(0.308) than non-adaptive GD(0.336).\\
-Test set error : GDad have bigger test error(0.359) than non-adaptive GD(0.328).\\
+Train set error : GDad have smaller train error(0.315) than non-adaptive GD(0.349).\\
+Test set error : GDad have bigger test error(0.353) than non-adaptive GD(0.323).\\
 \\
@@
 Spped : GDad reaches near the local minima faster than non-adaptive gradient.\\
-Train set error : GDad have smaller train error(0.209) than non-adaptive GD(0.323).\\
-Test set error : GDad have bigger test error(0.399) than non-adaptive GD(0.357).\\
+Train set error : GDad have smaller train error(0.303) than non-adaptive GD(0.333).\\
+Test set error : GDad have bigger test error(0.390) than non-adaptive GD(0.342).\\
 \\
@@
 
+\subsubsection{Scipy optimizer}
+\paragraph
+1 The following plots demonstrate the results of Logistic Regression using scipy.optimize, with iterations = 1000, learning rate $\eta$ = 1 and varying degrees $l$ = \{1, 2, 5, 15\}:
+\begin{figure}[h]
+	\includegraphics[width=0.4\textwidth]{scipy_1.png}
+	\caption{degree $l$ = 1}
+	\includegraphics[width=0.4\textwidth]{scipy_2.png}
+	\caption{degree $l$ = 2}
+	\includegraphics[width=0.4\textwidth]{scipy_5.png}
+	\caption{degree $l$ = 5}
+	\includegraphics[width=0.4\textwidth]{scipy_15.png}
+	\caption{degree $l$ = 15}
+\end{figure}
+\clearpage
+
+\paragraph
+2 These are the comparsion between GDad, non-adpative GD and scipy optimizer.\\
+\textbf{Degree $l$ = 1 :}\\
+Train set error : All have the same train error(0.469).\\
+Test set error : All have the same test error(0.387).\\
+\\
+\textbf{Degree $l$ = 2 :}\\
+Train set error : All have the same train error(0.450).\\
+Test set error : All have the same test error(0.354).\\
+\\
+\textbf{Degree $l$ = 5 :}\\
+Train set error : Scipy optimizer(0.295) $<$ GDad (0.315) $<$ GD(0.349).\\
+Test set error : Scipy optimizer(0.417) $>$ GDad(0.353) $>$ GD(0.323).\\
+\\
+\textbf{Degree $l$ = 15 :}\\
+Train set error : Scipy optimizer(0.210) $<$ GDad(0.303) $<$ GD(0.333).\\
+Test set error : Scipy optimizer(1.649) $<$ GDad (0.390) $<$ non-adaptive GD(0.342).\\
+\\
+Scipy optimizer optimizes the cost function better than the others.
+Therefore it has the lowest train set errors in all degrees.
+However, it has the highest test set error in all degrees.
+I think it is becuase of overfitting to the train set.
+Scipy optimizer makes a hypothesis fit perfectly to train set so it causes overfitting problem and get the highest test set error.\\
+\\
+It doesn't change my opinion that degree $l$ = 5 is best to fit the data.
+Low degree can not predict the complex hypothesis and high degree can cause the overfitting problem.
+Therfore, appropriate degree is the best.
+In this problem, it is 5.
+
 \end{document}

### 2018-04-17 paper/paper.tex
update the answer 2.2.3.2

@@
 \documentclass[a4paper]{article}
-\usepackage{amsmath, amssymb, bm}
+\usepackage{amsmath, bm}
 \usepackage[margin=1in]{geometry}
@@
 \subsection{Derivation of Regularized Linear Regression}
-\begin{itemize}
-  \item Preliminary questions
-    \begin{itemize}
-      \item for each i, \(\bm{X}^{(i)}\) is n+1 dimensional column vector. For
-        notaion convenience, all \(\bm{X}_0^{(i)}\) is set to \(0\).
-      \item The gradient of \(J(\bm{\theta})\) is \[
-          \frac{\partial J(\bm{\theta})}{\partial \bm{\theta}} = \langle
-          \frac{\partial J(\bm{\theta})}{\partial \theta_0}, \quad
-          \frac{\partial J(\bm{\theta})}{\partial \theta_1}, \quad
-          \cdots, \quad
-          \frac{\partial J(\bm{\theta})}{\partial \theta_n}
-          \rangle
-        \]. It is n+1 dimensional column vector.
-      \item In gradient, function \(f\) is
-        \(\mathbb{R}^n\rightarrow\mathbb{R} \) and the gradient itself is vector.
-        The jacobian matrix of function
-        \(\bm{f}\colon\mathbb{R}^n\rightarrow\mathbb{R}^m\) is
-        \[[
-          \quad \frac{\partial \bm{f}}{\partial x_1} \quad
-          \frac{\partial \bm{f}}{\partial x_2} \quad
-          \cdots \quad \frac{\partial \bm{f}}{\partial x_n} \quad
-          ] =
-          \begin{bmatrix}
-            \frac{\partial f_1}{\partial x_1} & \cdots & \frac{\partial f_1}{\partial x_n} \\
-            \vdots & \ddots & \vdots \\
-            \frac{\partial f_m}{\partial x_1} & \cdots & \frac{\partial f_m}{\partial x_n}
-          \end{bmatrix}
-          \]
-          where \(\bm{f} = <f_1, f_2, \cdots, f_m>\) and \(\bm{x} = <x_1, x_2, \cdots, x_n>\).
-          When \(m=0\), Jacobian matrix and gradient are same.
-        \item \(\bm{X\theta}\) is \(m\) dimension vector. The dimension of jacobian
-          matrix \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is \(n+1 \times m\).
-          In this case, \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is same with \(\bm{X}\).
-    \end{itemize}
-  \item 2
-  \item 3
-\end{itemize}
+asdfasdf
 
@@
 \paragraph
-5 One possible way to terminate the gradient descent is setting a threshold to the cost function.
-While caluating the cost in each iteration, if it is below the setting threshold, it can terminate the process.
-Using this way, it can not reach the perfect local minima but it can reach close to the local minima depending on the threshold.
-Therefore it can save time.
-If high accuracy is aimed, then set the threshold low.
-And if middle accuracy and high speeed are aimed, then set the threshold a little bit higher.
+5
+
 \subsubsection{Adaptative gradient descent (GDad)}

### 2018-04-17 paper/paper.tex
update the answer 2.2.1.5

@@
 \paragraph
-5
-
+5 One possible way to terminate the gradient descent is setting a threshold to the cost function.
+While caluating the cost in each iteration, if it is below the setting threshold, it can terminate the process.
+Using this way, it can not reach the perfect local minima but it can reach close to the local minima depending on the threshold.
+Therefore it can save time.
+If high accuracy is aimed, then set the threshold low.
+And if middle accuracy and high speeed are aimed, then set the threshold a little bit higher.
 \subsubsection{Adaptative gradient descent (GDad)}

### 2018-04-17 paper/paper.tex
1.1 question 2 answered
equeation env -> \[\]

--- 2018-04-17 paper/paper.tex
@@
     \end{itemize}
-  \item 2
+  \item When the gradient of the cost function is zero, the cost function is minimized.
+    \begin{align*}
+      \frac{\partial \bm{X\theta}}{\partial \bm{\theta}} = 0 \\
+      \frac{2}{m}(\bm{X\theta}-\bm{y})^T \cdot \bm{X} + \frac{2\lambda}{m}\bm{\theta} = 0 \\
+      \frac{2}{m}(\bm{X}^T\bm{X\theta} - \bm{X}^T\bm{y}) + \frac{2\lambda}{m}\bm{\theta} = 0 \\
+      \bm{X}^T\bm{X\theta} - \bm{X}^T\bm{y} + \lambda\bm{\theta} = 0 \\
+      \bm{X}^T\bm{X\theta} - \bm{X}^T\bm{y} + \lambda\bm{I\theta} = 0 \\
+      (\bm{X}^T\bm{X} + \lambda\bm{I})\bm{\theta} = \bm{X}^T\bm{y} \\
+      \bm{\theta} = (\bm{X}^T\bm{X} + \lambda\bm{I})^{-1}\bm{X}^T\bm{y}
+    \end{align*}
+    As long as \(\bm{X}^T\bm{X} + \lambda\bm{I}\) is invertable, the optimal parameters
+    \(\bm{\theta}^* = (\bm{X}^T\bm{X} + \lambda\bm{I})^{-1}\bm{X}^T\bm{y}\)
   \item 3
@@
 \subsection{Derivation of Gradient}
-\begin{equation}
+\[
   \begin{split}
@@
   \end{split}
-\end{equation}
+\]
 The partial derivative of the cost function with respect $\theta_j$ is
-\begin{equation}
+\[
   \begin{split}
@@
   \end{split}
-\end{equation}
-Thus, the gradient of the cost function is
-\begin{equation}
+\]
+Thus, the gradient of the cost function is \[
   \frac{\partial J(\bm{\theta})}{\partial \theta_j } = \frac{1}{m} \sum_{i=1}^m \left( h_{\bm{\theta}}(\bm{x}^{(i)}) - y^{(i)}\right) \cdot x_j^{(i)}
-\end{equation}
+\]
+
 \subsection{Logistic Regression training with gradient descent and scipy.optimize}

### 2018-04-19 main_poly.py
fixes error calculations

@@ -23,7 +23,7 @@ TODO boxes are to be found in 'poly.py'
 
 def main():
     # Set the degree of the polynomial expansion
-    degree = 20
+    degree = 15
     data_path = 'data_linreg.json'
 
     # Load the data

### 2018-04-19 plot_rbf.py

@@ -93,7 +93,7 @@ def plot_errors(i_best, n_centers, mse_train, mse_val, mse_test):
     #  - Don't forget to make everything readable with legend title
 
     for mse, lab in zip([mse_train, mse_val, mse_test], ['train', 'val', 'test']):
-        plt.plot(n_centers, mse/np.max(mse), label=lab, linewidth=3)
+        plt.plot(n_centers, mse, label=lab, linewidth=3)
 
     plt.ylim([0, 1])
     plt.axvline(x=n_centers[i_best], color='black', linestyle='--', linewidth=3,

### 2018-04-19 rbf.py

@@ -147,7 +147,7 @@ def compute_error(theta, n_centers, x, y):
 
     centers, sigma = get_centers_and_sigma(n_centers)
     X = design_matrix(x, centers, sigma)
-    err = np.linalg.norm(X.dot(theta) - y) ** 2
+    err = (1/x.shape[0]) * np.linalg.norm(X.dot(theta) - y) ** 2
 
     # END TODO
     ######################

### 2018-04-19 paper/paper.tex
typo. invertable -> invertible
completes sections 1.2 and 1.3

@@
     \end{align*}
-    As long as \(\bm{X}^T\bm{X} + \lambda\bm{I}\) is invertable, the optimal parameters
+    As long as \(\bm{X}^T\bm{X} + \lambda\bm{I}\) is invertible, the optimal parameters
     \(\bm{\theta}^* = (\bm{X}^T\bm{X} + \lambda\bm{I})^{-1}\bm{X}^T\bm{y}\)
@@
 \includegraphics[width=0.5\textwidth]{linreg_deg20.png}\par
+
+We found that the 27th degree polynomial had the lowest training error, although test error for degree 27 was 2.743.
+
+\includegraphics[width=\textwidth]{linreg_deg27.png}
+
+However, the degree with lowest validation error was 13.  Training error for the 13th degree polynomial was 0.384.
+
+\includegraphics[width=\textwidth]{linreg_deg13.png}
+
+The following graph depicts polynomial degree plotted against training, test, and validation error:
+
+\includegraphics[width=\textwidth]{linreg_error_plot.png}
+
+The graph makes a distinct 'U' shape with test and validation error.
+Errors generally decrease for the first 13 or so degrees as one would expect, since more powerful polynomials can more accurately model the complex dataset.
+However, these errors begin to increase again past the 13th degree due to overfitting.
+Overfitting is the process by which models adapt to specific features of the training set that are not present elsewhere, and becomes a problem as the model becomes less accurate for predicting new data.
+Overfitting is mitigated at smaller degrees, as models lack the explanatory power to model these specific features.
+Validation sets, constructed from the same dataset as training sets, are important to producing accurate models.
+The model is not trained on the validation set, and as a result the model's performance on the validation set is an accurate measure of overall performance, as well as an indicator of overfitting.
+By taking the polynomial degree with the lowest validation error, we can find the 'best' model that most accurately fits the data without overfitting.
+
+\subsection{Linear Regression with radial basis functions}
+
+The following plots demonstrate the results of Linear Regression with 1, 2, 5, and 20 RBF Kernels:
+
+\noindent
+\includegraphics[width=0.5\textwidth]{linreg_c1.png}%
+\includegraphics[width=0.5\textwidth]{linreg_c2.png}\\[2em]
+\includegraphics[width=0.5\textwidth]{linreg_c5.png}%
+\includegraphics[width=0.5\textwidth]{linreg_c20.png}\par
+
+We found that the model with 40 RBF Kernels had the lowest training error, although test error for 40 RBF Kernels was 182.
+
+\includegraphics[width=\textwidth]{linreg_c40.png}
+
+However, the number of RBF kernels with lowest validation error was 9.  Training error was 0.337.
+
+\includegraphics[width=\textwidth]{linreg_c9.png}
+
+The following graph depicts polynomial degree plotted against training, test, and validation error:
+
+\includegraphics[width=\textwidth]{linreg_rbf_error.png}
 

### 2018-04-19 rbf.py
minor tweak in rbf algorithm

@@ -76,7 +76,7 @@ def design_matrix(x, centers, sigma):
     # TIP: don't forget that the first row has only ones
     #
 
-    hbf_arrays = [x]
+    hbf_arrays = [np.ones(x.shape)]
     for c in centers:
         new_arr = np.exp(((x - c)**2 * -1) / (2 * sigma**2))
         hbf_arrays.append(new_arr)

### 2018-04-19 paper/paper.tex
additional paper updates

@@
 
-However, the degree with lowest validation error was 13.  Training error for the 13th degree polynomial was 0.384.
+However, the degree with lowest validation error was 13.  Test error for the 13th degree polynomial was 0.384.
 
@@
 
-However, the number of RBF kernels with lowest validation error was 9.  Training error was 0.337.
+However, the number of RBF kernels with lowest validation error was 9.  Testing error was 0.337.
 
@@
 \includegraphics[width=\textwidth]{linreg_rbf_error.png}
+
+We found that RBF models behaved similarly to polynomial models, but performed significantly better.
+The best fit of a polynomial model, polynomial degree 13, had an test error of 0.384, while the best RBF model, 9 Kernels, had a test error of 0.337.
+However, it should be noted that overfitting with higher numbers of parameters is much more severe with RBF models.
 

### 2018-04-19 paper/paper.tex
update the answer 2.2.1.1

--- 2018-04-17 paper/paper.tex
@@
 \subsection{Derivation of Regularized Linear Regression}
-\begin{itemize}
-  \item Preliminary questions
-    \begin{itemize}
-      \item for each i, \(\bm{X}^{(i)}\) is n+1 dimensional column vector. For
-        notaion convenience, all \(\bm{X}_0^{(i)}\) is set to \(0\).
-      \item The gradient of \(J(\bm{\theta})\) is \[
-          \frac{\partial J(\bm{\theta})}{\partial \bm{\theta}} = \langle
-          \frac{\partial J(\bm{\theta})}{\partial \theta_0}, \quad
-          \frac{\partial J(\bm{\theta})}{\partial \theta_1}, \quad
-          \cdots, \quad
-          \frac{\partial J(\bm{\theta})}{\partial \theta_n}
-          \rangle
-        \]. It is n+1 dimensional column vector.
-      \item In gradient, function \(f\) is
-        \(\mathbb{R}^n\rightarrow\mathbb{R} \) and the gradient itself is vector.
-        The jacobian matrix of function
-        \(\bm{f}\colon\mathbb{R}^n\rightarrow\mathbb{R}^m\) is
-        \[[
-          \quad \frac{\partial \bm{f}}{\partial x_1} \quad
-          \frac{\partial \bm{f}}{\partial x_2} \quad
-          \cdots \quad \frac{\partial \bm{f}}{\partial x_n} \quad
-          ] =
-          \begin{bmatrix}
-            \frac{\partial f_1}{\partial x_1} & \cdots & \frac{\partial f_1}{\partial x_n} \\
-            \vdots & \ddots & \vdots \\
-            \frac{\partial f_m}{\partial x_1} & \cdots & \frac{\partial f_m}{\partial x_n}
-          \end{bmatrix}
-          \]
-          where \(\bm{f} = <f_1, f_2, \cdots, f_m>\) and \(\bm{x} = <x_1, x_2, \cdots, x_n>\).
-          When \(m=0\), Jacobian matrix and gradient are same.
-        \item \(\bm{X\theta}\) is \(m\) dimension vector. The dimension of jacobian
-          matrix \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is \(n+1 \times m\).
-          In this case, \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is same with \(\bm{X}\).
-    \end{itemize}
-  \item When the gradient of the cost function is zero, the cost function is minimized.
-    \begin{align*}
-      \frac{\partial \bm{X\theta}}{\partial \bm{\theta}} = 0 \\
-      \frac{2}{m}(\bm{X\theta}-\bm{y})^T \cdot \bm{X} + \frac{2\lambda}{m}\bm{\theta} = 0 \\
-      \frac{2}{m}(\bm{X}^T\bm{X\theta} - \bm{X}^T\bm{y}) + \frac{2\lambda}{m}\bm{\theta} = 0 \\
-      \bm{X}^T\bm{X\theta} - \bm{X}^T\bm{y} + \lambda\bm{\theta} = 0 \\
-      \bm{X}^T\bm{X\theta} - \bm{X}^T\bm{y} + \lambda\bm{I\theta} = 0 \\
-      (\bm{X}^T\bm{X} + \lambda\bm{I})\bm{\theta} = \bm{X}^T\bm{y} \\
-      \bm{\theta} = (\bm{X}^T\bm{X} + \lambda\bm{I})^{-1}\bm{X}^T\bm{y}
-    \end{align*}
-    As long as \(\bm{X}^T\bm{X} + \lambda\bm{I}\) is invertable, the optimal parameters
-    \(\bm{\theta}^* = (\bm{X}^T\bm{X} + \lambda\bm{I})^{-1}\bm{X}^T\bm{y}\)
-  \item 3
-\end{itemize}
+asdfasdf
 
@@
 \subsection{Derivation of Gradient}
-\[
+\begin{equation}
 \begin{split}
@@
 \end{split}
-\]
+\end{equation}
 The partial derivative of the cost function with respect $\theta_j$ is
-\[
+\begin{equation}
 \begin{split}
@@
 \end{split}
-\]
-Thus, the gradient of the cost function is \[
+\end{equation}
+Thus, the gradient of the cost function is
+\begin{equation}
 \frac{\partial J(\bm{\theta})}{\partial \theta_j } = \frac{1}{m} \sum_{i=1}^m \left( h_{\bm{\theta}}(\bm{x}^{(i)}) - y^{(i)}\right) \cdot x_j^{(i)}
-\]
-
+\end{equation}
 \subsection{Logistic Regression training with gradient descent and scipy.optimize}
@@
 \paragraph
-1The function check\_gradient in toolbox.py is here to test if your gradient is well computed. Explain what it is doing
+1 The function check\_gradient in toolbox.py is to test if the gradient is well computed.\\ \\
+The process of the gradient is like this.\\  \\
+1) Init the point x0 using random function\\
+2) Compute the cost f0 of x0 in a given dataset\\
+3) Compute the gradient g0 of x0 in a given dataset\\
+4) Init dx using random function\\
+5) Compute df\_g(that is, df is obtained by my gradient fucntion) by inner product of dx and g0\\ \\
+for deltas=(1e-2, 1e-4, 1e-6), iterate 6) $-$ 8)\\
+6) Compute the cost f1 of point (x0 + delta * dx)\\
+7) Compute df(that is, df is obtatined by the two points difference) between point x0 and point (x0 + delta * dx)\\
+8) Compute the "df error" by using the formula = np.log10(np.abs(df\_g - df) + 1e-20) and store the value in the array "apporx\_err"\\ \\
+9) check\_gradient function checks "np.diff(approx\_err) $<$ -1).all()".\\
+
+If my gradient function works well, "df error" should be close to 0.
+Also, because the deltas are small and differnt values for each iteration, each df is calulated as a slightly different value from the other df for each iteration.
+Therfore, for each iteration, "df error" is close to 0 and each "df error" is sligtly different because of different delta values.
+Therefore, np.diff(approx\_err) should be lower than -1.
+
+What if my gradient function doesn't work well?
+In this case, np.diff(approx\_err) cannot be lower than -1.
+Because, if my gradient funcition doesn't work well, df\_g and df are differnt so "df error" should not be close to 0.
+Also, because the delta is so small, each df should be slightly different for each iteration.
+Therfore, "df error = df\_g - df" should not close to 0 and should be slightly different.
+If "df error"s are not close to 0 and slighly differnt from each other, they can not satisfy the condition "np.diff(approx\_err) $<$ -1).all()".
+
 \paragraph

### 2018-04-19 paper/paper.tex
update the answer 2.2.2.4

@@
 \paragraph
-4
+4 These are  good pairs of values for the number of iterations and learning rate for each degree in l ∈{1,2,5,15} that provides a good solution in reasonable time\\
+\textbf{Degree $l$ = 1 :}\\
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{best_fit_degree1.png}
+	\includegraphics[width=0.5\textwidth]{best_fit_degree1_error.png}
+	\caption{learing rate $\eta$ = 1, iteration = 100}
+\end{figure}\\
+\textbf{Degree $l$ = 2 :}\\
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{best_fit_degree2.png}
+	\includegraphics[width=0.5\textwidth]{best_fit_degree2_error.png}
+	\caption{learing rate $\eta$ = 0.5, iteration = 700}
+\end{figure}
+\textbf{Degree $l$ = 5 :}\\
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{best_fit_degree5.png}
+	\includegraphics[width=0.5\textwidth]{best_fit_degree5_error.png}
+	\caption{learing rate $\eta$ = 0.5, iteration = 2000}
+\end{figure}
+\textbf{Degree $l$ = 5 :}\\
+\begin{figure}[h]
+	\includegraphics[width=0.5\textwidth]{best_fit_degree15.png}
+	\includegraphics[width=0.5\textwidth]{best_fit_degree15_error.png}
+	\caption{learing rate $\eta$ = 0.5, iteration = 2000}
+\end{figure}
+
+Among those four degrees, the degree 5 has the lowest test set error.
+Therfore, degree 5 is best to fit the given dataset.
+
 \paragraph

### 2018-04-20 main_poly_model_selection.py
removes obsolete TODO comments

@@ -45,22 +45,9 @@ def main():
     for i in range(K):
         theta_list[i], mse_train[i], mse_val[i], mse_test[i] = poly.train_and_test(data, degrees[i])
 
-    ######################
-    #
-    # TODO
-    #
-    # Find the best degree that minimizes the validation error.
-    # Store it in the variable i_best for plotting the results
-    #
-    # TIPs:
-    # - use the argmin function of numpy
-    # - the code above is already giving the vectors of errors
     i_best = np.argmin(mse_val)
     best_degree = degrees[i_best]
     best_theta = theta_list[i_best]
-    #
-    # END TODO
-    ######################
 
     # Plot the training error as a function of the degrees
     plot_errors(i_best, degrees, mse_train, mse_val, mse_test)

### 2018-04-20 plot_rbf.py

@@ -81,17 +81,6 @@ def plot_errors(i_best, n_centers, mse_train, mse_val, mse_test):
     :return:
     """
 
-    ######################
-    #
-    # TODO
-    #
-    # Plot with the Mean Square Error as a function of the number of centers
-    # Use a different color for each sets: train, validation and test
-    # Your are welcome to adapt the code used for the polynomial feature expansion
-    #
-    # Tips:
-    #  - Don't forget to make everything readable with legend title
-
     for mse, lab in zip([mse_train, mse_val, mse_test], ['train', 'val', 'test']):
         plt.plot(n_centers, mse, label=lab, linewidth=3)
 
@@ -101,7 +90,3 @@ def plot_errors(i_best, n_centers, mse_train, mse_val, mse_test):
     plt.xlabel('Degrees')
     plt.ylabel('MSE')
     plt.legend()
-
-    #
-    # END TODO
-    ##############

### 2018-04-20 rbf.py

@@ -27,21 +27,8 @@ def get_centers_and_sigma(n_centers):
     :return:
     """
 
-    ######################
-    #
-    # TODO
-    #
-    # TIPs:
-    #   - Use the linspace function from numpy
-    #   - ATTENTION: You might want to write the division a / b, with a and b integers but in python 2 this will perform
-    #       an euclidian division. The solution is to convert one of the two integers to float.
-    #
-
     centers = np.linspace(-1.0, 1.0, n_centers)
     sigma = 2.0 / n_centers
-
-    # END TODO
-    ######################
 
     return centers, sigma
 
@@ -65,26 +52,12 @@ def design_matrix(x, centers, sigma):
     :return: Expanded data in a numpy array of shape (N,n_centers+1)
     """
 
-    ######################
-    #
-    # TODO
-    #
-    # Return the numpy array of shape (N,n_centers+1)
-    # Storing the data of the form exp(- (x_i - c_j) ^2 / (2 sigma^2) ) at row i and column j+1
-    # Look at the function description for more info
-    #
-    # TIP: don't forget that the first row has only ones
-    #
-
     hbf_arrays = [np.ones(x.shape)]
     for c in centers:
         new_arr = np.exp(((x - c)**2 * -1) / (2 * sigma**2))
         hbf_arrays.append(new_arr)
 
     res = np.hstack(hbf_arrays)
-
-    # END TODO
-    ######################
 
     return res
 
@@ -101,23 +74,9 @@ def train(x, y, n_centers):
     :return: numpy array containing the coefficients of each polynomial degree in the regression
     """
 
-    ######################
-    #
-    # TODO
-    #
-    # Returns the analytical solution of the linear regression
-    #
-    # TIPs:
-    #   - Don't forget to first expand the data
-    #   - This should not be very different from the solution you provided in poly.py
-    #
-
     centers, sigma = get_centers_and_sigma(n_centers)
     X = design_matrix(x, centers, sigma)
     theta_opt = np.linalg.inv(X.T.dot(X)).dot(X.T.dot(y))
-
-    # END TODO
-    ######################
 
     return theta_opt
 
@@ -134,23 +93,9 @@ def compute_error(theta, n_centers, x, y):
     :return: err: Mean square error
     """
 
-    ######################
-    #
-    # TODO
-    #
-    # Returns the error (i.e. the cost function)
-    #
-    # TIPs:
-    #   - Don't forget to first expand the data
[…]

### 2018-04-20 paper/paper.tex
Resolve the conflict

@@
 \paragraph
-2The following plots demonstrate the results of Logistic Regression with degree 1 and learning rate $\eta$ = 1 for 20 and 2000 iterations :
+2 The following plots demonstrate the results of Logistic Regression with degree 1 and learning rate $\eta$ = 1 for 20 and 2000 iterations :
 
+\paragraph
+\\
 \begin{figure}[h]
@@
 \end{figure}
-\clearpage
 \begin{figure}[h]
@@
 3 The following plots demonstrate the results of Logistic Regression with degree = 2 , iterations = 200 and learning rate $\eta$ = \{.15, 1.5, 15.\} :
+\clearpage
 \begin{figure}[h]
-	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta015.png}
-	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta015_error.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta015.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta015_error.png}
 	\caption{learing rate $\eta$ = .15}
 \end{figure}
-\clearpage
 \begin{figure}[h]
-	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta105.png}
-	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta105_error.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta105.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta105_error.png}
 	\caption{learing rate $\eta$ = 1.5}
@@
 \begin{figure}[h]
-	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta15.png}
-	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta15_error.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta15.png}
+	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta15_error.png}
 	\caption{learing rate $\eta$ = 15}
@@
 4 These are  good pairs of values for the number of iterations and learning rate for each degree in l ∈{1,2,5,15} that provides a good solution in reasonable time\\
+\clearpage
 \textbf{Degree $l$ = 1 :}\\
@@
 \end{figure}\\
-\textbf{Degree $l$ = 2 :}\\
+\textbf{Degree $l$ = 2 :}
 \begin{figure}[h]
@@
 \end{figure}
-\textbf{Degree $l$ = 5 :}\\
+\clearpage
+\textbf{Degree $l$ = 5 :}
 \begin{figure}[h]
@@
 	\caption{learing rate $\eta$ = 0.5, iteration = 2000}
-\end{figure}
-\textbf{Degree $l$ = 5 :}\\
+\end{figure}\\
+\textbf{Degree $l$ = 15 :}\\
 \begin{figure}[h]
